### 2017-10-14 Gruba/06-perf.tex

\stitle{Exp-4: Case Study for Feature Extraction}
In this section, we show the results of our demo system for user features extraction.
Considering the huge amount of users, we carefully selected one typical user for analysis.
Here we chose Mary(a famous drama and movie actress in China) as an example.
The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
Mary has more followers than followees.
The Sina Microblog tag she made for herself is ``actress'' (演员).
As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
Mary's short-term interest, e.g. from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵). So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.

>>>>

\stitle{Exp-4: Case Study for Feature Extraction}
In this test, we show the results of our demo system for user features extraction.
%
Considering the huge amount of users, we carefully selected one typical user for analysis.
Here we chose Mary (a famous drama and movie actress in China) as an example.

The feature extraction result for Mary is depicted in Fig.\ \ref{fig:userFeatures}.
Then we can see the basic information of Mary in Sub-Fig.\ \ref{fig:userFeatures:uf-1}: her nickname is Actress Mary (演员马丽) and she is from Beijing (北京).
Mary has more followers than followees.
The Sina Microblog tag she made for herself is ``actress'' (演员).
As to the long-term interest, she is interested with stage performance (舞台表演), drama (话剧表演),film (电影光影) and so on as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-2}, which is consistent with her tag.
The probability distribution of tweeting and retweeting indicates that she is more active at night than daytime as shown in Sub-Fig.\ \ref{fig:userFeatures:uf-3} and \ref{fig:userFeatures:uf-4}.
According to Sub-Fig.\ \ref{fig:userFeatures:uf-5} and \ref{fig:userFeatures:uf-6}, the interval between her two tweeted/retweeted microblogs is mostly within 48 hours, showing she is an active user.
Mary's short-term interest, e.g. from 09/01/2016 to 09/30/2016, is shown in Sub-Fig.\ \ref{fig:userFeatures:uf-7}, which indicates she had been busy with promoting the drama ``Earl of Oolong Mountain'' (乌龙山伯爵). So the results are in line with expectations, as drama (话剧) and stage (舞台) in Sub-Fig.\ \ref{fig:userFeatures:uf-7}.

### 2017-10-14 Gruba/07-rela.tex
v4.3
v4.3

In this section, we shall review related work in literature mainly from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basic info, behavior and interest.

>>>>

In this section, we review related work in literature from the aspects of analyzing features, mining groups and modeling behavior within the realm of social network modeling.
As aforementioned, \sys{} leverages the user features of basics, behavior and interest.
